---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jastyle

<!-- badges: start -->
<!-- badges: end -->

The goal of jastyle is to ...

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("januaryadvisors/jastyle")
```
## Font

The package uses [Onest](https://fonts.google.com/specimen/Onest) as its base font. Onest is registered automatically on package load via `sysfonts::font_add_google("Onest")` and `showtext::showtext_auto()`, so no manual install is needed.
```{r check font}
library(jastyle)
ja_font()
```

## Use ggplot theme_ja()

```{r cars}
library(tidyverse)
ggplot(iris) +
  geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species), size=3) +
  ggtitle("Title here", subtitle = "Subtitle here") +
  labs(caption = "Source: Add source here.") +
  theme_ja() 
```


## Use highcharter ja_hc_theme()
```{r, out.width = 800, screenshot.opts = list(vwidth = 800, vheight = 500)}
library(highcharter)
highcharter::hchart(iris, "scatter", hcaes(Sepal.Length, Sepal.Width, color=Species)) %>%
  hc_title(text = "Title here") %>%
  hc_subtitle(text = "Subtitle here.") %>%
  hc_caption(text = "<strong>Source</strong>: Source here.") %>%
  hc_add_theme(ja_hc_theme())
```


## Custom ja_colors
### View colors
```{r}

ja_view_colors()

```

### Apply manual color palette
```{r}
ggplot(iris) +
  geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species), size=3) +
  ggtitle("Title here", subtitle = "Subtitle here") +
  labs(caption = "Source: Add source here.") +
  scale_color_manual(
    values = c(ja_hex("blue"), ja_hex("orange"), ja_hex("green"))
  ) +
  theme_ja()
```


